---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(aws.apireference)
```

# aws.apireference

<!-- badges: start -->
[![R build status](https://github.com/jonthegeek/aws.apireference/workflows/R-CMD-check/badge.svg)](https://github.com/jonthegeek/aws.apireference/actions)
[![Codecov test coverage](https://codecov.io/gh/jonthegeek/aws.apireference/branch/master/graph/badge.svg)](https://codecov.io/gh/jonthegeek/aws.apireference?branch=master)
<!-- badges: end -->

The goal of aws.apireference is to help us validate our aws.* packages vs the API documentation.

## Installation

This package is unlikely to ever have a CRAN version.

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("jonthegeek/aws.apireference")
```
## Examples

### Actions and Functions

AWS APIs contain a number of actions in `CamelCase`. 
`aws.*` packages tend to have `snake_case` functions to invoke those actions.
This package has three functions to deal with that relationship.

```{r ec2-actions}
# Get the list of available actions for the EC2 API.
ec2_actions <- get_actions("ec2")
head(ec2_actions)
```

```{r expected-functions}
# Convert those actions to function names.
expected_functions <- get_expected_functions(ec2_actions)
head(expected_functions)
```

```{r check-package-functions}
# check_package_functions uses those functions to figure out what a package has
# and what it theoretically should have. Note: You must have the aws.ec2 package
# installed for this example.
ec2_check <- check_package_functions("ec2")

# For simplicity I'm cutting out a few hundred missing functions.
ec2_check$missing_functions <- head(ec2_check$missing_functions)
ec2_check
```

## Code of Conduct

Please note that the aws.apireference project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.
